Implementing Real-Time Transport Services over an Ossified Network

### 2016-05-23 paper.tex
intro edits and comment

Real-time applications are increasingly important in the Internet.
We want to make it easier to write these applications, while improving
the quality of experience for users of those applications by lowering
latency and increasing robustness.
In this, we are challenged by the limitations of the standard Internet
transport protocols, and by the ossified nature of the network, which makes
it increasingly difficult to deploy new transports.

@@

In practice, the only protocols that can be widely used in the Internet are
TCP and UDP. Other protocols are blocked by firewalls and other middleboxes.
TCP provides sophisticated congestion control, coupled with a reliable,
ordered, byte stream API. These are suitable for many applications, but are
not necessarily appropriate for real-time traffic.  UDP exposes the best-effort
IP packet delivery service, offering flexibility to develop new protocols,
but at the cost of requiring completely new protocol mechanisms to be
defined. Both protocols are usable for real-time applications, but neither
really provides the right services and API.  This forces each application
to re-invent mechanisms that should be provided by the transport, increasing
costs and complexity, raising barriers to innovation.

@@

In this paper we discuss the appropriate set of transport services and APIs
for real-time applications.
We demonstrate that it is possible to realise these services and APIs
in the context of both TCP and UDP, despite the limitations imposed by the
legacy protocols, middleboxes, and ossification of the network.
We present initial results to show that, despite the observed ossification,
the network has the flexibility to deploy new transport protocols, if care
is taken to reinterpret layer boundaries and deploy those new transports in
the context of TCP and UDP.

@@

Our contributions are to identify the needs of real-time applications, and
the appropriate transport services and APIs to support those needs;
to illustrate how those transport services can be realised on the current
Internet, in the context of UDP and TCP deployments; and
to present some initial measurement results to show that the mechanisms we
propose ought to be usable in the public Internet.

@@

We begin, in Section \ref{sec:services} by discussing transport services
for real-time applications, and outlining the common conceptual API that
those applications use.
This is followed, in Section \ref{sec:ossification}, by a review of the
deployment considerations for new protocols, caused by ossification of
the network, with Section \ref{sec:partial} considering, in particular, how
TCP reliability semantics can evolve within the constraints of the deployed
infrastructure.
Section \ref{sec:realising} outlines how the transport services we have
identified can be realised in practical networks.
Finally, Section \ref{sec:related} discusses related work, and Section
\ref{sec:conclusions} concludes.

>>>>

Real-time applications are increasingly
%important
present in the Internet.
%We want to make it easier to write these applications
Such applications should be easier to program, while also improving
the quality of experience for users.
 %of those applications
by lowering latency and increasing robustness.
%In this, we are
This limitations of standard Internet transport protocols makes this a
challenging target. Moreover, the ossified nature of the network makes
it increasingly difficult to deploy new transports.

@@

In practice, only UDP and TCP are widely usable in the Internet,
since remaining protocols are blocked by firewalls and other
middleboxes. UDP exposes the best-effort IP packet delivery service,
offering the flexibility to develop new protocols. The high costs
associated involve defining completely new protocol mechanisms. In
contrast TCP mechanisms are well defined, consisting of sophisticated
congestion control coupled with a reliable, ordered, byte stream API.
These are proven suitable for many applications, but are inappropriate
for real-time traffic. While both protocols may be used for real-time
applications, neither really provides the right services and API. This
forces each application to re-invent or re-interpret mechanisms that
should be provided by the transport. The increased costs and
complexity of doing so raise barriers to innovation.

@@

In this paper we identify and present the appropriate set of transport
services and APIs for real-time applications, and demonstrate their
merit by implementing a proof-of-concept. We show that it is possible
to realise real-time services and APIs in the context of both TCP and
UDP, despite the limitations imposed by their legacies, and by
middleboxes, and ossification of the network.  Initial experiments
with our implementation suggest that
%to show that, despite network ossification,
the network has the flexibility to deploy new transport protocols,
provided care is taken to reinterpret layer boundaries that respect
conventional UDP and TCP.\todo{I can infer the meaning of previous sentence having worked on the problem; otherwise may be very ambiguous to the reader.}
%and deploy those new transports in the context of TCP and UDP.

@@

% Our contributions
In doing so we make three main contributions. First, we make explicit
the needs of real-time applications, as well as the appropriate
transport services and APIs to support those needs. Second, we
illustrate an example realisation of those transport services on the
current Internet, in the context of UDP and TCP deployments. Finally,
we present initial measurement results that suggest the proposed
mechanisms ought to be usable in the public Internet.

@@

We begin in Section \ref{sec:services} by discussing transport
services for real-time applications, and outlining the common
conceptual API that those applications use. This is followed in
Section \ref{sec:ossification} by a review of deployment
considerations for new protocols, caused by ossification of the
network. Section \ref{sec:partial} considers, in particular, how TCP
reliability semantics can evolve within the constraints of the
existing infrastructure. The semantics are realised and put into
practice in Section \ref{sec:realising}.
% outlines how the transport services we have identified can be
% realised in practical networks.
Finally, Section \ref{sec:related} discusses related work, and Section
\ref{sec:conclusions} concludes.
